---
title: "Project 1 Data 607"
author: "Maryluz Cruz"
date: "9/19/2019"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Assignment

In this project, you’re given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players:

Player’s Name, Player’s State, Total Number of Points, Player’s Pre-Rating, and Average Pre Chess Rating of Opponents

For the first player, the information would be:

Gary Hua, ON, 6.0, 1794, 1605

1605 was calculated by using the pre-tournament opponents’ ratings of 1436, 1563, 1600, 1610, 1649, 1663, 1716, and dividing by the total number of games played.

##Include the Package Stringr

In order to to this assignment we need to include the package stringr

```{r}
require(stringr)
```

##Insert Table into R

In order to do that I entered the .txt file into my github repository and I read in the url. 

```{r}
tournament_info <- readLines("https://raw.githubusercontent.com/Luz917/tournamentinfo/master/tournamentinfo.txt", warn=FALSE)##this was needed because it gave a warning about incomplete final line 
```

Head of the table

```{r}
head(tournament_info)
```

Tail of the Table

```{r}
tail(tournament_info)
```

##Cleaning the table 

We clean the table removing all lines with --------- and the column names, to get ready for the extractions. 

```{r}
tournament_c<-unlist(str_extract_all(tournament_info,"[:alpha:]+.{2,}"))
tournament_c<-tournament_c[c(3:130)]
head(tournament_c)
```

##Player ID

First step is to get the Player ID. Since all the player id numbers were removed I have to input the string. I may have cleaned it too much. 

```{r}
player_id<-c(1:64)
player_id
```

##Players Name

Next we extract all of the players names. 

```{r}
pname<-unlist(str_extract_all(tournament_c,"[:alpha:]+(\\s\\w+ ([:alpha:])*[:alpha:]*)"))
pname<-str_trim(pname,side = "right")##this removes the spacing 
pname
```

##Player's State

Next step is to extraxct the players state. 

```{r}
state<-unlist(str_extract_all(tournament_c,"\\b^[:alpha:]{2}\\b"))
state
```

##Player's Points

Next step we extract all of the player's points.

```{r}
points<-unlist(str_extract_all(tournament_c,"[:digit:][:punct:][:digit:]"))
points
```

##Player's Pre Rating 

Next we have to get the players pre rating. This is a little more complicated since we have to distinguish between the pre and the post rating and the only way to do that is to include R: in the extraction. But since some of the ratings are not four numbers or include a P and a few numbers after it I decided to do each case by step until all are 3 to four letters. 

```{r}
pre_rating<-unlist(str_extract_all(tournament_c,"R:\\s+[:alnum:]*"))
pre_rating<-str_replace_all(pre_rating,"R:","")##this removes the R:
pre_rating<-str_replace_all(pre_rating,"P\\d+","") ##this removes P and the numbers follewed by the P
pre_rating<-str_trim(pre_rating,side = "both")
pre_rating
```

##Average Opponet Rating

This is the part where I get confused and was unable to calculate the average opponet rating, but I did extract the wins and losses. 

```{r}
wins_losses<-unlist(str_extract_all(tournament_c,"\\w \\s\\d+"))
head(wins_losses)##shows the first player 
tail(wins_losses)##shows the last player
```

##Create the final table 

We have to put the extracted data and join them to create the columns and make a data frame.

```{r}
final_table_chess<-data.frame(player_id,pname, state, points,pre_rating)
head(final_table_chess)
```

##Create the csv file.

```{r}
write.csv(final_table_chess,"Final_Table_Chess.csv",row.names = FALSE)
read.csv("Final_Table_Chess.csv")
```



